On the surprising effectiveness of a simple matrix exponential derivative approximation, with application to global SARS-CoV-2

### 2023-09-13 manuscript/revision_letter.tex
updated phylogenetic tree

\begin{reply}
content...
\end{reply}

\begin{enumerate}	
\setcounter{enumi}{7}	
	\item 
	The proposed method is able to include higher-dimension rate matrix compared with \citet{lemey2009bayesian,lemey2014unifying} [1, 2]. Can the authors then have an external comparison to the results in \citet{lemey2020accommodating} just visually to see whether the color pattern in the phylogenetic tree is matched?
\end{enumerate}

>>>>

\setcounter{figure}{3}
\begin{figure*}[!t]
	\centering
	\includegraphics[width=0.7\textwidth]{figures/summary2.tree.pdf}
	\vspace{-0.5em}
	\caption{Posterior predictive modes for (unobserved) ancestral
		locations color a phylogenetic tree that describes the
		shared evolutionary history of 285 SARS-CoV-2
		samples.}\label{fig:tree}
\end{figure*}

\begin{reply}
We have updated Figure \ref{fig:tree} to the best of our ability to make the main geographic blocks visible.  The previous limitation to 29 regions was caused by software limitation that our updated figure also avoids.
\end{reply}

\begin{enumerate}	
\setcounter{enumi}{7}	
	\item 
	The proposed method is able to include higher-dimension rate matrix compared with \citet{lemey2009bayesian,lemey2014unifying}. Can the authors then have an external comparison to the results in \citet{lemey2020accommodating} just visually to see whether the color pattern in the phylogenetic tree is matched?
\end{enumerate}
